### 2020-02-19 README.Rmd
remove target_value at creation
Fixing the problem of oolong_tm without topic intrusion tests

Removal of inadviable workflow

A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.

@@

As instructed, put back the score you would like to validate into the `docvars` "target_value". In this example, we calculate the AFINN score for each tweet using quanteda. The dictionary `afinn` is bundle with this package.

@@

```{r}
docvars(gold_standard, "target_value") <- all_afinn_score
summarize_gold_standard(gold_standard)
```

@@

### Inadvisable workflow

*NOTE: This workflow is not recommended!*

This workflow violates the "validation first" principle. You can supply the `target_value` at the creation of oolong test.

```{r, include = FALSE}
set.seed(46709394)
```

```{r}
dfm(trump2k, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
           base = ntoken(trump2k, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
    pull(afinn_score) -> trump2k_afinn_score
oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive", target_value = trump2k_afinn_score)
oolong_test
```

```{r, include = FALSE}
oolong_test$.__enclos_env__$private$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
```

```{r}
oolong_test$lock()
gold_standard <- oolong_test$turn_gold()
docvars(gold_standard, "target_value")
```

```{r}
summarize_gold_standard(gold_standard)
```

>>>>

A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer'.

@@

In this example, we calculate the AFINN score for each tweet using quanteda. The dictionary `afinn` is bundle with this package.

@@

```{r}
summarize_oolong(oolong_test, target_value = all_afinn_score)
```

@@
